---
title: "Data Prep"
author: "Sonali Syngal"
date: "27 September 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preperation
```{r}
library(dplyr)
df <- read.csv("database.csv", header = TRUE)



names_to_drop <- c( 'Record.ID', 'Agency.Name', 'Record.Source', 
                   'Perpetrator.Ethnicity') # Dropping the variables from our analysis


#Our main dataset:
murder.num <- df %>%
  filter(Crime.Type == "Murder or Manslaughter") %>%
  select(-one_of(names_to_drop)) %>%
  filter(Victim.Age > 0 & Victim.Age < 99) %>%
  filter(!(Perpetrator.Race == 'Unknown' & Crime.Solved == 'Yes')) %>%
  mutate(Victim.Counts = Victim.Count + 1, Perpetrator.Counts = Perpetrator.Count +1) %>%
  select(-one_of('Victim.Count', 'Perpetrator.Count'))


#Summarizing each city and the number of crimes in it:
most_crime_cities <- 
  group_by(murder.num, City) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) 

#This will print cities with the maximum number of crimes. We will look at the first 5:
head(most_crime_cities) 

```
It seems that LA, Cook, Harris, Wayne and New York are cities in which most crime is committed.



```{r}

# This will give us an additional column which will have proportion of crimes solved in that city
prop_crimes_solved <- 
  group_by(murder.num, City) %>% 
  mutate(TotalCrimes = n()) %>%
  ungroup() %>%
  filter(Crime.Solved == "Yes") %>%
  group_by(City) %>%
  mutate(Prop.Crimes.Solved= (n()/TotalCrimes)) %>% 
  arrange(TotalCrimes)
# However this dataset isnt the total dataset since Crime Solved = No has been filtered out


max_crime_cities <- c('New York', 'Los Angeles','Cook','Harris', 'Wayne')


#Creating a table of our cities with proportion of crime solved and total crimes:
prop.table <- select(prop_crimes_solved, City, TotalCrimes,Prop.Crimes.Solved ) %>%
  filter(City %in% max_crime_cities) %>%
  group_by(City, TotalCrimes, Prop.Crimes.Solved) %>%
  summarise() 

prop.table
```


## New York : Individual City Analysis

```{r}

#Preparing data for your individual city-wise analysis:
new_york <- filter(murder.num, City == "New York") #You can filter your individual city. For eg, City == "Cook"
```



What we can do in each city (Analysis):
1) Logistical regressions to check what variables determine ability of case being solved or not. 
2) Monthly/ Yearly analysis on cases
3) Victim Sex, Victim Age distribution (same with perpretrator)
4) Perpretrator and victim race relationship
5) Relationship distribution
6) Weapon distribution
7) Correlate victim age and perp age
8) Victim count versus pepretrator count (lol?)
9) Hypothesis testing on anything which seems relevant 
10) Provide suggestions to help in preventing crimes and solving crimes

These are just some I have identified, we should all do as much and whatever we feel like might get great results.

#Running Logistical regression Syntax:
```{r}
LRM <- glm(Crime.Solved ~Victim.Age, family = 'binomial', data= new_york) #Run with various variables and see relationship- Whether any variable predicts Crime.Solved.
```

#Random correlation test:
```{r}
cor(new_york$Victim.Age, new_york$Perpetrator.Age)
```
Not so high correlation, but positive. What is a high correlation?






